systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-06-05 paper/branches/useR2006/Poster/systemfit_poster.tex
Poster for useR! 2006: added box "Motivation"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@669 591db2bd-e0a0-4d22-8c19-2192dbb7da31

% \fbox{
\begin{postercolumn}{0.49}
% Features
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Features}}
{\standardfontsize
\begin{itemize}
\item several estimation methods, e.g.:
\begin{itemize}
\item Ordinary Least Squares (OLS)
\item Two-Stage Least Squares (2SLS)
\item Seemingly Unrelated Regression (SUR)
\item Three-Stage Least Squares (3SLS)
\end{itemize}
\item imposition of linear restrictions by two different methods
\item instrumental variables: the same for all equations or different for each equation
\item several different formulas to calculate the residual covariance matrix
\item several different formulas for the 3SLS estimation
\item $t$ tests: degrees of freedom of the whole system
or degrees of freedom of the single equation
\item OLS/2SLS estimation: different $\sigma^2$s for each single equation
or the same $\sigma^2$ for all equations
\item wrapper function for (classical) panel-like data in long format
(\texttt{systemfitClassic})
\item testing linear hypothesis using the F-, Wald-, and LR-statistic
\item Hausman test for the consistency of the 3SLS estimator
\end{itemize}
}}

>>>>

% \fbox{
\begin{postercolumn}{0.49}
% Motivation
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Motivation}}
{\standardfontsize
\begin{itemize}
\item many theoretical models consist of more than one equation\\
$\Rightarrow$ contemporaneously correlation of disturbance terms (likely)\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   simultaneously estimation of all equations as 
   °Seemingly Unrelated Regression° (SUR) leads to efficient results}
\mbox{}
\item theoretically derived cross-equation parameter restrictions\\
$\Rightarrow$ simultaneous estimation of all equations required
\item endogeneity of some variables\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   estimation using °Two-Stage Least Squares° (2SLS)
   or °Three-Stage Least Squares° (3SLS) required}
\end{itemize}
}}

% Features
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Features of \texttt{systemfit}}}
{\standardfontsize
\begin{itemize}
\item several estimation methods, e.g.:
\begin{itemize}
\item Ordinary Least Squares (OLS)
\item Two-Stage Least Squares (2SLS)
\item Seemingly Unrelated Regression (SUR)
\item Three-Stage Least Squares (3SLS)
\end{itemize}
\item imposition of linear restrictions by two different methods
\item instrumental variables: the same for all equations or different for each equation
\item several different formulas to calculate the residual covariance matrix
\item several different formulas for the 3SLS estimation
\item $t$ tests: degrees of freedom of the whole system
or degrees of freedom of the single equation
\item OLS/2SLS estimation: different $\sigma^2$s for each single equation
or the same $\sigma^2$ for all equations
\item wrapper function for (classical) panel-like data in long format
(\texttt{systemfitClassic})
\item testing linear hypothesis using the F-, Wald-, and LR-statistic
\item Hausman test for the consistency of the 3SLS estimator
\end{itemize}
}}
